ROMS solves the primitive equations in an Earth-centered
rotating environment, based on the Boussinesq approximation and
hydrostatic vertical momentum balance. ROMS is discretized in
coastline- and terrain-following curvilinear coordinates.
ROMS is a split-explicit, free-surface ocean model, where short time steps
are used to advance the surface elevation and barotropic momentum, with a
much larger time step used for temperature, salinity, and baroclinic momentum.
ROMS employs a special 2-way time-averaging procedure for the barotropic mode,
which satisfies the 3D continuity equation \citep{Shc03b}.
The specially designed predictor-corrector time step algorithm used in ROMS
allows a substantial increase in the permissible time-step size.

ROMS has been designed to be optimized on shared memory parallel computer
architectures such as the SGI/CRAY Origin 2000. Parallelization is done
by two dimensional sub-domains partitioning. Multiple sub-domains can be
assigned to each processor in order to optimize the use of processor
cache memory. This allow super-linear scaling when performance growth even
faster than the number of CPUs.

The third-order, upstream-biased advection scheme implemented in ROMS
allows the generation of steep gradients, enhancing the effective resolution
of the solution for a given grid size \citep{Shc98}. Explicit lateral
viscosity is null everywhere in the model domain except in sponge layers
near the open  boundaries where it increases smoothly close to the lateral
open boundaries.

A non-local, K-profile planetary (KPP) boundary layer scheme \citep{Lar94}
parameterizes the unresolved physical vertical subgrid-scale processes.
If a lateral boundary faces the open ocean, an active, implicit,
upstream biased, radiation condition connects the model solution
to the surroundings \citep{Mar01}.
