\section{CPP-keys description : cppdefs.h} \label{cppkeydesc} 


In this section, we present the differents cpp keys used to define the numerical or
physical options in ROMS\_AGRIF. These latters are ordered in differents sections and
described in Table \ref{tab:cppkeys1}.
%------------------------------

\begin{longtable}
   {|p{0.5\linewidth}|p{0.5\linewidth}|}
   \hline
    TYPE & CPP KEYS NAME \\ 
   \endfirsthead
   \hline
   TYPE & CPP KEYS NAME \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 
%    \hline \\
% %    \multicolumn{2}{|p{0.6666\linewidth}|}{C'est fini} \\
%    \hline
   \endlastfoot 
\hline

%-------------------------------------------
                 &                      \\
\underline{TEST CASE}      &                      \\
                 &        BASIN           \\
                 &        CANYON\_A       \\
                 &        CANYON\_B       \\
                 &        GRAV\_ADJ       \\
                 &        INNERSHELF      \\
                 &        OVERFLOW        \\
                 &        SEAMOUNT        \\
                 &        SHELFRONT       \\
                 &        SOLITON         \\
                 &        UPWELLING       \\
                 &        INTERNAL        \\
                 &        VORTEX          \\
                 &        REGIONAL : realistric configuration   \\
%------------------------------------------
\hline
\multicolumn{2}{|p{1\linewidth}|}{\centering Basic options} \\
\hline

Configuration Name &                \\
&  BENGUELA \\


Parallelization    &                      \\
                   &    OPENMP            \\
                   &    MPI               \\


Embedding          &                      \\
                   &         AGRIF        \\
                   &         AGRIF\_2WAY  \\


Open Boundary Conditions  &                \\
 &  TIDES                     \\
 &  OBC\_EAST                 \\
 &  OBC\_WEST                 \\
 &  OBC\_NORTH                \\
 &  OBC\_SOUTH                \\


Tides &                \\
& TIDES      \\
& SSH\_TIDES  \\
& UV\_TIDES   \\
& TIDERAMP   \\


Applications          &                     \\
&    BIOLOGY              \\
&    FLOATS               \\
&    STATIONS             \\
&    PASSIVE\_TRACER      \\
&    SEDIMENT  \\
&    BBL  \\
& \\
\hline
\multicolumn{2}{|p{1\linewidth}|}{\centering More advanced options} \\

\hline
Parallelization         &                      \\
& PARALLEL\_FILES  \\
& AUTOTILING       \\
& ETALON\_CHECK     \\

Model dynamics         &                      \\
&  SOLVE3D                    \\
&  UV\_COR                    \\
&  UV\_ADV                    \\

Grid configuration     &                      \\
&    CURVGRID          \\
&    SPHERICAL         \\
&    MASKING            \\

Lateral Momentum Mixing     &                      \\
&                        MIX\_GP\_UV \\
&                        MIX\_GP\_UV \\
&                        UV\_VIS2 \\
&                        UV\_VIS4 \\
&                        VIS\_SMAGO \\

Lateral Tracer Mixing     &                      \\
&                       MIX\_GP\_TS \\
&                       MIX\_S\_TS \\
&                       MIX\_EN\_TS \\
&                       TS\_DIF2 \\
&                       TS\_DIF4 \\
&                       TS\_SPLIT\_UP3 \\

Nudging         &                      \\
&                        ZNUDGING \\
&                        M2NUDGING \\
&                        M3NUDGING \\
&                        TNUDGING \\
&                        ROBUST\_DIAG \\


Vertical Mixing      &                      \\
&                     BODYFORCE  \\
&                     BVF\_MIXING  \\
&                     LMD\_MIXING  \\
&                     LMD\_SKPP  \\
&                     LMD\_BKPP  \\
&                     LMD\_RIMIX  \\
&                     LMD\_CONVEC  \\
&                     LMD\_DDMIX  \\
&                     LMD\_NONLOCAL  \\

Equation of State      &                      \\
&                        SALINITY  \\
&                        NONLIN\_EOS  \\
&                        SPLIT\_EOS  \\

Surface Forcing     &                      \\
&                        QCORRECTION \\
&                        SFLX\_CORR \\
&                        DIURNAL\_SRFLUX \\
&                        BULK\_FLUX \\
&                        BULK\_FAIRALL \\
&                        BULK\_LW \\
&                        BULK\_EP \\
&                        BULK\_SMFLUX \\

Sponge Layer     &                      \\
&                        SPONGE \\

Lateral Forcing  &                      \\ 
 &                      \\ 
\textit{1-Climatology strategy : 3D fields covering the  whole domain }  &           \\
&                        CLIMATOLOGY \\
&                        ZCLIMATOLOGY \\
&                        M2CLIMATOLOGY \\
&                        M3CLIMATOLOGY \\
&                        TCLIMATOLOGY \\
& \\
\textit{2-Boundary strategy : 1D fields only on OBC points} &       \\
&                        FRC\_BRY \\
&                        Z\_FRC\_BRY \\
&                        M2\_FRC\_BRY \\
&                        M3\_FRC\_BRY \\
&                        T\_FRC\_BRY \\

Bottom Forcing     &                     \\
&                        ANA\_BSFLUX \\
&                        ANA\_BTFLUX \\

Point Sources - Rivers     &                      \\
&                        PSOURCE \\
&                        ANA\_PSOURCE  \\

Open Boundary Conditions     &                      \\
&                        OBC\_M2SPECIFIED \\
&                        OBC\_M2FLATHER \\
&                        OBC\_M2CHARACT \\
&                        OBC\_M2ORLANSKI \\
&                        OBC\_VOLCONS \\
&                        OBC\_M3ORLANSKI \\
&                        OBC\_M3SPECIFIED \\
&                        OBC\_TORLANSKI \\
&                        OBC\_TSPECIFIED \\

Input/Output and Diagnostics     &               \\
&     AVERAGES                  \\
&     AVERAGES\_K                \\
&     DIAGNOSTICS\_TS            \\
&     DIAGNOSTICS\_TS\_ADV        \\
&     DIAGNOSTICS\_TS\_MLD        \\
&     DIAGNOSTICS\_UV \\

BIOLOGY models     &               \\
&  PISCES         \\
&  BIO\_NChlPZD    \\
&  BIO\_N2P2Z2D2   \\
&  BIO\_N2ChlPZD2  \\

%-------------------------------------------
\hline

%--------------------------------------------------------------
\caption{Description of the CPP keys used in the cppdefs.h file}
\label{tab:cppkeys1}
\end{longtable}

\subsection*{Test Case}

\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEYS NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEYS NAME  & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 

   \endlastfoot 
\hline
%-------------------------------------------
BASIN & Must be defined for running the Basin Example.   \\
CANYON\_A & Must be defined for running the Canyon\_A Example.   \\
CANYON\_B  & Must be defined for running the Canyon\_B Example.    \\
GRAV\_ADJ & Must be defined for running the Gravitational Adjustment Example.   \\
INNERSHELF & Must be defined for running the Inner Shelf Example.   \\
OVERFLOW & Must be defined for running the Gravitational/Overflow Example.   \\
SEAMOUNT & Must be defined for running the Seamount Example.   \\
SHELFRONT & Must be defined for running the Shelf Front Example.     \\
SOLITON &  Must be defined for running the Equatorial Rossby Wave Example.  \\
UPWELLING & Must be defined for running the Upwelling Example.   \\
INTERNAL &  Must be defined for running the Internal tides example.  \\
VORTEX & Must be defined for running the Baroclinic Vortex Example.   \\
REGIONAL & Must be defined if running realistic regional simulations.   \\



%-------------------------------------------
\hline

\caption{Test Case related CPP keys}
\label{tab:cppkeysTestCase}
\end{longtable}

\subsection*{Parallelization}

\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEYS NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEYS NAME  & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 

   \endlastfoot 
\hline
%-------------------------------------------
OPENMP & Activate the Open-MP parallelization protocol.      \\
MPI & Activate the MPI parallelization protocol.   \\
PARALLEL\_FILES & Activate the I/O writing on multiprocessor.    \\
AUTOTILING & Activate the subdomains partitionning optimization.    \\
%-------------------------------------------
\hline
\caption{Parallelization related CPP keys}
\label{tab:cppkeysparallelization}
\end{longtable}

\paragraph{Preselected options } \\
\noindent
\# ifdef MPI \\
\# $~$$~$undef PARALLEL\_FILES \\
\# endif \\
\# undef AUTOTILING \\


\subsection*{Embedding}
\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME  & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 

   \endlastfoot 
\hline
%-------------------------------------------
AGRIF & Activate the (1-WAYS) nesting capabilities.   \\
AGRIF\_2WAY & Add the the 2-WAYS nesting (update of the parent grid solution by the child
grid solution) capabilities.   \\
%-------------------------------------------
\hline

\caption{Embedding related CPP keys}
\label{tab:cppkeyNesting}
\end{longtable}

\subsection*{Open Boundary Conditions I }

\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME  & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 

   \endlastfoot 
\hline
%-------------------------------------------
OBC\_EAST & Open eastern boundary.    \\
OBC\_WEST & Open western boundary.   \\
OBC\_SOUTH & Open southern boundary.     \\
OBC\_NORTH & Open northern boundary.    \\
%-------------------------------------------
\hline

\caption{Open Boundary Conditions (basic) related CPP keys}
\label{tab:cppkeysOBCbasic}
\end{longtable}



\subsection*{Tides}

\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME  & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 

   \endlastfoot 
\hline
%-------------------------------------------
TIDES & Activate the forcing og tides at open-boundaries.  \\
SSH\_TIDES & Define for processing sea surface elevation tidal data at the model boundaries.   \\
UV\_TIDES &  Define for processing ocean current tidal data at the model boundaries.  \\
TIDERAMP & Apply a ramping of the tidal current, (in general 2 days) at
initialization.
Warning! This should be off when restarting the model.   \\
%-------------------------------------------
\hline
\caption{Tides forcing related CPP keys}
\label{tab:cppkeysTides}
\end{longtable}


\paragraph{Preselected options } \\
\noindent
\# ifdef TIDES \\
\#  define SSH\_TIDES \\
\#  define UV\_TIDES\\
\#  define TIDERAMP \\ 
\# endif \\




\newpage
\subsection*{Applications}

\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME  & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 

   \endlastfoot 
\hline
%-------------------------------------------
BIOLOGY        &  Activate the biogeochemical module.  \\
FLOATS         &  Activate floats.  \\
STATIONS       &  Store model outputs for each time step at different station locations.  \\
PASSIVE\_TRACER & Add a passive tracer.   \\
SEDIMENT       &  Activate the sediment module.  \\
BBL            &  Activate the bottom boundary layer module.  \\
%-------------------------------------------
\hline

\caption{related CPP keys}
\label{tab:cppkeysApplication}
\end{longtable}

\paragraph{Preselected options: } \\
\noindent
\# undef BIOLOGY \\
\# undef FLOATS \\
\# undef STATIONS \\
\# undef PASSIVE\_TRACER \\
\# undef SEDIMENT \\
\# undef BBL \\

\subsection*{Model dynamics}

\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 
   \endlastfoot 

%-------------------------------------------
\hline
SOLVE3D  & Define if solving 3D primitive equations.     \\
UV\_COR  & Activate Coriolis terms.    \\
UV\_ADV  & Activate advection terms.   \\
\hline
%-------------------------------------------

\caption{Model dynamics related CPP keys}
\label{tab:cppkeysSurForc}
\end{longtable}


\paragraph{Preselected options: } \\
\noindent
\# define SOLVE3D\\ 
\# define UV\_COR \\
\# define UV\_ADV \\
\# ifdef TIDES \\
\# $~~$ define SSH\_TIDES \\
\# $~~$ define UV\_TIDES \\
\# $~~$ define TIDERAMP \\
\# endif


\subsection*{Grid configuration}

\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 
   \endlastfoot 

%-------------------------------------------
\hline
CURVGRID  & Activate curvilinear coordinate grid option.   \\
SPHERICAL & Activate longitude/latitude grid positioning.   \\
MASKING   & Activate land masking in the domain. \\
\hline
%-------------------------------------------
\caption{Model grid related CPP keys}
\label{tab:cppkeysGrid}
\end{longtable}


\paragraph{Preselected options:  } \\
\noindent
\# define CURVGRID \\
\# define SPHERICAL \\
\# define MASKING \\

\subsection*{Lateral Momentum Mixing}
\
\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME  & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 

   \endlastfoot 
\hline
%-------------------------------------------
MIX\_GP\_UV & Activate mixing on geopotential (constant Z) surfaces.     \\
MIX\_S\_UV & Activate mixing on iso-sigma (constant sigma) surfaces.   \\
UV\_VIS2 & Activate Laplacian horizontal mixing of momentum. \\
UV\_VIS4 & Activate Bilaplacian horizontal mixing of momentum. \\
%-------------------------------------------
\hline

\caption{Lateral Momentum mixing related CPP keys}
\label{tab:cppkeysLateralMomentumMixing}
\end{longtable}

\paragraph{Preselected options: }  \\
\noindent
\# define UV\_VIS2 \\
\# define MIX\_GP\_UV  \\


\subsection*{Lateral Tracer mixing}

\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME  & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 
   \endlastfoot 
\hline
%-------------------------------------------
MIX\_GP\_TS & Activate mixing on geopotential (constant Z) surfaces. \\
MIX\_S\_TS &  Activate mixing on iso-sigma level surfaces.  \\
MIX\_EN\_TS & Activate mixing on isopygnal level surfaces.   \\
TS\_DIF2 &  Activate Laplacian horizontal mixing of tracer.  \\
TS\_DIF4 &  Activate Bilaplacian horizontal mixing of tracer.  \\
TS\_SPLIT\_UP3 & Activate the rotated split upstream advection-diffusion scheme for
tracer equation.
\citep{Marches09} \\
%-------------------------------------------
\hline

\caption{Lateral Tracer mixing related CPP keys}
\label{tab:cppkeysLateralTracerMixing}
\end{longtable}

\paragraph{Preselected options: }  \\
\noindent 
\# define MIX\_GP\_TS \\
\# define TS\_DIF2 \\
\# undef TS\_SPLIT\_UP3 \\

\newpage
\subsection*{Nudging}

\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME  & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 

   \endlastfoot 
\hline
%-------------------------------------------
ZNUDGING    &  Activate nudging layer for zeta.   \\
M2NUDGING   &  Activate nudging layer for barotropic velocities.   \\
M3NUDGING   &  Activate nudging layer for baroclinic velocities.   \\
TNUDGING    &  Activate nudging layer for tracer.   \\
ROBUST\_DIAG & Activate strong tracer nudging in the interior for diagnostic simulations.  \\

%-------------------------------------------
\hline
\caption{Nudging related CPP keys}
\label{tab:cppkeysNudging}
\end{longtable}

The nudging layer has the same location than sponge layer. In the sponge/nudging
layer, the signal, tracers and momentum, is nudged towards climatology using a
nudging coefficient $\tau_{out}$ expressed in $s{-1}$, equal to the inverse of the
coefficient $TauM_{out}/TauT_{in}$ in the namelist roms.in

\paragraph{Preselected options: }  \\
\noindent
\# define CLIMATOLOGY \\
\# ifdef CLIMATOLOGY \\
..... \\
\#  $~$$~$define ZNUDGING \\ 
\#  $~$$~$define M2NUDGING \\ 
\#  $~$$~$define M3NUDGING \\ 
\#  $~$$~$define TNUDGING \\ 
\#  $~$$~$undef ROBUST\_DIAG \\ 
\# endif \\


\subsection*{Vertical Mixing}

\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME  & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 

   \endlastfoot 
\hline
%-------------------------------------------
BODYFORCE & Define if applying surface and bottom stresses as bodyforces   \\
BVF\_MIXING & Activate a simple mixing scheme based on the Brunt-V\"ais\"al\"a frequency   \\
LMD\_MIXING & Activate Large/McWilliams/Doney mixing (LMD-KPP closure)   \\
LMD\_SKPP &  Activate surface boundary layer KPP mixing (LMD-KPP closure)  \\
LMD\_BKPP &  Activate bottom boundary layer KPP mixing (LMD-KPP closure)  \\
LMD\_RIMIX & Activate shear instability interior mixing (LMD-KPP closure)   \\
LMD\_CONVEC & Activate convection interior mixing (LMD-KPP closure)     \\
LMD\_DDMIX & Activate double diffusion interior mixing (LMD-KPP closure)   \\
LMD\_NONLOCAL & Activate nonlocal transport (LMD-KPP closure)   \\
%-------------------------------------------
\hline

\caption{Vertical mixing related CPP keys}
\label{tab:cppkeysVerticalMixing}
\end{longtable}
\paragraph{Preselected options: }  \\
\noindent
\# undef BODYFORCE \\
\# undef BVF\_MIXING \\ 
\# define LMD\_MIXING \\
\# ifdef LMD\_MIXING \\
\# $~$$~$ define LMD\_SKPP \\
\# $~$$~$ define LMD\_BKPP \\
\# $~$$~$ define LMD\_RIMIX \\
\# $~$$~$ define LMD\_CONVEC \\
\# $~$$~$ undef LMD\_DDMIX \\
\# $~$$~$ undef LMD\_NONLOCAL \\
\# endif \\

\subsection*{Equation of state}
\begin{longtable}{|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 
   \endlastfoot 

%-------------------------------------------
\hline
SALINITY   & Define if using salinity.   \\
NONLIN\_EOS & Activate the nonlinear equation of state.   \\
SPLIT\_EOS  & Activate the split of the nonlinear equation of state in a
adiabatic part and a compressible part for the reduction of pressure gradient errors
\citep{Shc03a}.   \\
\hline
%-------------------------------------------
\caption{Equation of state related CPP keys}
\label{tab:cppkeyEqState}
\end{longtable}


\paragraph{Preselected options: } \\
\noindent
\# define SALINITY \\
\# define NONLIN\_EOS \\
\# define SPLIT\_EOS \\

\subsection*{Surface Forcing}
\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 
   \endlastfoot 

%-------------------------------------------
\hline
BULK\_FLUX & Activate the bulk parametrization. \\
BULK\_EP &  Activate the bulk parametrization for salinity fluxes. \\
BULK\_LW & Activate online long-wave radiation calculation using model SST. \\
BULK\_SMFLUX & Activate the bulk parametrization for surface momentum stress. \\
QCORRECTION & Activate net heat flux correction. \\
SFLX\_CORR &  Activate freshwater flux correction. \\
DIURNAL\_SRFLUX & Activate diurnal modulation of the short wave radiation flux. \\
%BULK\_WVEC & Compute the wind speed amplitude from the wind speed vector (uwnd and vwnd)
%read in the bulk file. \\
%BULK\_WSTR & Activate the bulk parametrization for wind stress calculation. Compute
%the windstress (sustr and svstr) from the wind speed vector, mentioned above.  \\
\hline
%-------------------------------------------

\caption{Surface forcing related CPP keys}
\label{tab:cppkeysSurForc}
\end{longtable}

\paragraph{Preselected options: }  \\
\noindent
\# define QCORRECTION \\
\# define SFLX\_CORR \\
\# define DIURNAL\_SRFLUX \\
\# undef BULK\_FLUX \\
\# ifdef BULK\_FLUX \\
\# $~$$~$define LW\_ONLINE \\ 
\# $~$$~$define BULK\_EP  \\
\# $~$$~$undef BULK\_SMFLUX \\
\# $~$$~$define DIURNAL\_SRFLUX \\
\# else \\
\# $~$$~$define QCORRECTION \\
\# $~$$~$define SFLX\_CORR \\
\# $~$$~$define DIURNAL\_SRFLX \\
\# endif \\


\subsection*{Sponge Layer}
\begin{longtable}{|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME  & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 

   \endlastfoot 
\hline
%-------------------------------------------
SPONGE &  Activate areas of enhanced viscosity/diffusion close to the 
lateral open boundaries.   \\

%-------------------------------------------
\hline

\caption{Sponge layer related CPP keys}
\label{tab:cppkeysSpongeLayer}
\end{longtable}



\subsection*{Lateral forcing}
\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME  & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 

   \endlastfoot 
\hline
%-------------------------------------------
CLIMATOLOGY &  Activate processing of climatology data.  \\
ZCLIMATOLOGY & Activate processing of  sea surface height climatology.   \\
M2CLIMATOLOGY & Activate processing of  barotropic velocities climatology.   \\
M3CLIMATOLOGY & Activate processing of  baroclinic velocities climatology.   \\
TCLIMATOLOGY &  Activate processing of tracer climatology.  \\
%-------------------------------------------
\hline
FRC\_BRY &  Activate direct boundary forcing   \\
Z\_FRC\_BRY & Activate boundary forcing for zeta.   \\
M2\_FRC\_BRY & Activate boundary forcing for barotropic velocities.   \\
M3\_FRC\_BRY & Activate boundary forcing for baroclinic velocities   \\
T\_FRC\_BRY &  Activate boundary forcing for tracers.  \\
\hline

\caption{Lateral forcing related CPP keys}
\label{tab:cppkeysLateralForcing}
\end{longtable}


\paragraph{Preselected options: }  \\
\noindent
\# define CLIMATOLOGY \\
\# ifdef CLIMATOLOGY \\ 
\# $~$ define ZCLIMATOLOGY \\
\# $~$ define M2CLIMATOLOGY \\
\# $~$ define M3CLIMATOLOGY \\
\# $~$ define TCLIMATOLOGY \\
\# $~$ ... \\
\# endif \\
 \\
\# undef FRC\_BRY \\
\# ifdef FRC\_BRY \\
\#  $~$define Z\_FRC\_BRY \\
\#  $~$define M2\_FRC\_BRY \\
\#  $~$define M3\_FRC\_BRY \\
\#  $~$define T\_FRC\_BRY \\
\# endif \\


%\hrule
\subsection*{Bottom forcing}
\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME  & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 

   \endlastfoot 
\hline
%-------------------------------------------
ANA\_BSFLUX & Define if using analytical bottom salinity flux     \\
ANA\_BTFLUX &  Define if using analytical bottom temperature flux.\\ 
%-------------------------------------------
\hline

\caption{Bottom forcing related CPP keys}
\label{tab:cppkeysBottomForcing}
\end{longtable}

\paragraph{Preselected options: }  \\
\noindent
\# define ANA\_BSFLUX \\ 
\# define ANA\_BTFLUX \\


\subsection*{Point Sources - Rivers}

\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME  & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 

   \endlastfoot 
\hline
%-------------------------------------------
PSOURCES & Define if using point sources (rivers)     \\
ANA\_PSOURCES & Define if using analytical vertical profiles for the point sources
(using fluxes defined in roms.in)  \\

%-------------------------------------------
\hline

\caption{Point Sources and Rivers related CPP keys}
\label{tab:cppkeysRivers}
\end{longtable}

\paragraph{Preselected options: }  \\
\noindent
\# undef PSOURCE \\ 
\# undef ANA\_PSOURCE

%\hrule


\subsection*{Open Boundary Conditions  II }
\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME  & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 

   \endlastfoot 
%\hline
%-------------------------------------------
OBC\_VOLCONS &  Activate mass conservation enforcement at open boundaries.          \\
OBC\_M2SPECIFIED & Activate specified open boundary conditions for ubar and vbar.   \\
OBC\_M2ORLANSKI & Activate 2D radiation open boundary conditions for ubar and vbar. \\
OBC\_M2FLATHER  & Activate Flather open boundary conditions for ubar and vbar.      \\
OBC\_M2CHARACT &  Activate open boundary conditions based on characteristic methods. \\
OBC\_M3SPECIFIED &  Activate specified open boundary conditions for u and v.  \\
OBC\_M3ORLANSKI & Activate 2D radiation open boundary conditions for u and v.    \\
OBC\_M3CHARACT &  Activate open boundary conditions based on characteristic methods 
for u and v.    \\
OBC\_TSPECIFIED &  Activate specified open boundary conditions for tracers.   \\
OBC\_TORLANSKI &   Activate 2D radiation open boundary conditions for tracers.   \\
OBC\_TUPWIND &     Activate upwind open boundary conditions for tracers.   \\
%-------------------------------------------
\hline

\caption{Open Boundary Condition related CPP keys}
\label{tab:cppkeysOBC}
\end{longtable}


\paragraph{Preselected options: }  \\
\noindent
\# ifdef TIDES \\
\#$~$ define OBC\_M2FLATHER \\ 
\# else \\
\#$~$ undef OBC\_M2SPECIFIED \\
\#$~$  undef OBC\_M2FLATHER \\
\#$~$  define OBC\_M2CHARACT \\
\#$~$  undef OBC\_M2ORLANSKI\\ 
\#$~$  ifdef OBC\_M2ORLANSKI \\
\#$~$$~$ define OBC\_VOLCONS \\
\#$~$  endif \\
\# endif \\
\# define OBC\_M3ORLANSKI \\
\# define OBC\_TORLANSKI \\
\# undef OBC\_M3SPECIFIED \\
\# undef OBC\_TSPECIFIED \\


\subsection*{Input - Output and Diagnostics}
\begin{longtable}
   {|p{0.30\linewidth}|p{0.7\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 
   \endlastfoot 

%-------------------------------------------
\hline
AVERAGES & Define if writing out time-averaged data.   \\
AVERAGES\_K & Define if writing out time-averaged vertical mixing.   \\
DIAGNOSTICS\_TS  & Define if writing out tendency terms for the tracer equations.   \\
DIAGNOSTICS\_TS\_ADV  & Activate advection formulation for tendency term for the
tracer equations.   \\
DIAGNOSTICS\_TS\_MLD  & Activate integration over the mixed-layer (MLD) for the
tendency term for the tracer equation.\\
DIAGNOSTICS\_UV & Define if writing out tendency terms for the momentum equations.   \\
\hline
%-------------------------------------------

\caption{I/O related CPP keys}
\label{tab:cppkeysIODiag}
\end{longtable}

\paragraph{Preselected options: } \\
\noindent
\# define AVERAGES \\
\# define AVERAGES\_K \\
\# undef DIAGNOSTICS\_TS \\
\# undef DIAGNOSTICS\_UV \\
\# ifdef DIAGNOSTICS\_TS \\
\# $~~$undef DIAGNOSTICS\_TS\_ADV \\
\# $~~$undef DIAGNOSTICS\_TS\_MLD \\
\# endif \\


\subsection*{Biology models}
\begin{longtable}
   {|p{0.25\linewidth}|p{0.75\linewidth}|}
   \hline
    CPP KEY NAME & Description \\ 
   \endfirsthead
   \hline
    CPP KEY NAME  & Description \\ 
   \hline
   \endhead
   \hline
   \multicolumn{2}{|p{0.6666\linewidth}|}{\textit{Next page}$\rightarrow$} \\
   \hline
   \endfoot 

   \endlastfoot 
\hline
%-------------------------------------------
PISCES          & Activate PISCES biogeochemical model          \\
BIO\_NChlPZD     & Activate idealized 4 compartiments NPZD type model  \\
BIO\_N2PZD2      & Activate idealized 6 compartiments NPZD type model   \\
BIO\_N2ChlP2Z2D2 & Activate idealized 8 compartiments NPZD type model \\
%-------------------------------------------
\hline
\caption{Biology model  related CPP keys}
\label{tab:cppkeysbiomodel}
\end{longtable}
\paragraph{Preselected options: } \\
\noindent
\# ifdef BIOLOGY \\
\# $~~$ undef PISCES \\
\# $~~$ define BIO\_NChlPZD \\
\# $~~$ undef BIO\_N2P2Z2D2 \\
\# $~~$ undef BIO\_N2ChlPZD2 \\
\# endif \\